\section{Ideas}
    \begin{enumerate}
        \item Jiju: Generate viva rubrics and viva questions for a given coding problem.
        \item Jiju: record viva or interview and generate score as per coding problem.
        \item Jiju: record interview and genearte fairness score as per the rubrics.
        \item Jiju: record viva and generate score for non tech skills like communication skills, soft skills, english fluency, grammer.
        \item Jiju: Educative chatbots
        \item generate list of classes given pipeline stage for a task. This will help coding
        \begin{enumerate}
            \item Vector DB Indexing pipeline\\
            Load file $\rightarrow$  Extract raw text $\rightarrow$  Normalize text $\rightarrow$  Create document (text + metadata) $\rightarrow$  Chunk document $\rightarrow$  Enrich chunks with metadata $\rightarrow$  Generate embeddings for chunks $\rightarrow$  Store embeddings in vector store 
            \item Vector DB Indexing pipeline\\
            Receive user query $\rightarrow$ Normalize / preprocess query $\rightarrow$ Generate embedding for query $\rightarrow$ Retrieve top-K relevant chunks $\rightarrow$ Assemble context from retrieved chunks $\rightarrow$ Build prompt (context + question) $\rightarrow$ Call LLM $\rightarrow$ Post-process LLM response $\rightarrow$ Return final answer (optionally with sources)
        \end{enumerate}
        \item Jiju: Ask chatgpt about - generative AI projects in education.
        \item Technique to create distractors for mcq. 
        \item generate rubrics and questions for practical
        \item ixl AI application
        \item multiple agents/llms based valuation of a question with each agent has seprate roles. 
        \item Multimodal valuation system. Aggregate (mean / median / majority)
        \item convert student answer and actaul answer into embedding and check similarity.
        \item start with 2 sentences from user answer and let ML predict next word. if the next word matches next word of users answer then mark it as match. count total matches and then perform grading.
        \item valuation using bottom up approach. Read the answer and try to find what question its answereing, what topic it is discussing.
        \item generate/seprate useless/wrong sentences from the answers and then grade using LLM. Compare the results.
        \item create a valuation system/framework and compare the results of 2 different LLMs.
        \item conduct an experiment by asking llm to valuate same question, answr, rubric many time and record if reponse is same. do this for various llms.
        \item filter and mark sentences with same meaning written again and again in answer paper.
        \item extract useful sentences from the answer by removing wrong/repeated/useless sentences then valuate the answer.
        \item extract sentences that contradict each other in the students answer.
        \item map each line in the answer to a rubric and then grade.
        \item Coding
        \begin{enumerate}
            \item generate an AI app that will help student write code. start with problem/project statement then designing directory structure and class files with contain comments about what they will do.
            \item when you designed a GUI app(Chat PDF Aman) using PyQt6. You created a list of events in md file. that file can be generated to valuate students Code for  PyQt6 python apps.
        \end{enumerate}     
        \item n8m workflow automation for teacher daily works and office management.  
        \item Generate a list of questions, LOs needed to understand a given topic in maths. content generaton. 
        \item Use the technique presented in MCQ gen paper to create(generate) explanation/tutorial of a research paper. 
        \item Improve mcqGen for multiple correct choices, currently it has only one correct answers.
        \item Propose RAG for MCQ, fill in the blank or other types of questions.
        \item Propose chunking stratgy for  MCQ, fill in the blank or other types of questions.
        \item Propose  a preprocessing step for MCQ, fill in the blank or other types of questions.
        \item method to extract topics, keywords, important phrases etc from a given lesson text. Ask chatgpt what algorithm it uses to extract topics, keywords, important phrases etc from a given lesson text. Do some innovation in it.
        \item do a comparative study about 2 techniques in RAG process for generating MCQ.
        \item propose  a methods to extract topics/keywords/correct answers and distractors for mcq generation.
        \item  generate a list of questions to understand a topic.
        \item propose a new prompt creation technique to extract MCQs.
        \item give a chapter of CBSE subjects EVS, Moral science, english and generate questions and compare with CBSE books.
        \item Content generation in hindi given a english text.
        \item MCQ generation based on gaps identified for an essay written by student
        \item given an MCQ question using RAG to find alternate multiple choice options.
        \item generate concepts which forms the basis for multiple choice MCQs.
        \item generate keywords, topics using iterative self refining steps and CoT. 
        \item generate code in a programming language written in different language.
        \item Generate a list of tools/methods/methodologies used in a research paper.
        \item Generate Flowchart/Steps/Algorithm/Pipeline-stages from a research paper.
        \item Generate test cases for a given coding problem. \cite{Lee2025}
        \item generate code given class and methods with comments explaining the task to be done.
        \item evaluate students idea before writing code based on the his comments explanation the code.
        \item evaluate students understranding of a given code based on his comments before every line.       
    \end{enumerate}
