\section{Stage-13: Self-Refine MCQ Refinement}
    \begin{enumerate}
        \item \textbf{Description:} This stage applies an iterative self-refinement process where the Large Language Model (LLM) critiques and improves its own previously generated MCQs. The MCQGen paper explicitly highlights the use of self-critique and correction to enhance question quality, clarity, difficulty, and distractor plausibility through cycles of feedback and revision, aligning with expert evaluations. \textcolor{green}{\textbf{[EXPLICIT]}}
        
        \item \textbf{Input:} 
        \begin{itemize}
            \item Refined MCQs generated in Stage-12. \textcolor{red}{\textbf{[INFERRED]}}
            \item Expert-driven prompt engineering templates that guide the self-critique and correction process. \textcolor{green}{\textbf{[EXPLICIT]}}
        \end{itemize}
        
        \item \textbf{Output:} 
        \begin{itemize}
            \item Iteratively improved MCQs rated higher for quality and educational value, ready for final validation. \textcolor{red}{\textbf{[INFERRED]}}
        \end{itemize}
        
        \item \textbf{Tool/Method/Algorithm:} 
        \begin{itemize}
            \item Multiple iterative API calls to the LLM where each call provides feedback on previous output and requests corrections. \textcolor{red}{\textbf{[INFERRED]}}
            \item Automatic metrics and expert-aligned scoring guides to evaluate and guide refinement. \textcolor{green}{\textbf{[EXPLICIT]}}
        \end{itemize}
        
        \item \textbf{Process:} Extract an MCQ from the list and perform the following iterative steps:
          \begin{itemize}  
              \item Use scoring guides and expert prompts to solicit critique from the LLM on each MCQ component (question stem, correct answer, distractors). \textcolor{green}{\textbf{[EXPLICIT]}}
              \item Generate corrections based on the LLM critique feedback via a separate API call. \textcolor{green}{\textbf{[EXPLICIT]}}
              \item repeat above 2 steps until quality thresholds are met or maximum iterations reached. \textcolor{red}{\textbf{[INFERRED]}}
          \end{itemize}

      \end{enumerate}