\documentclass[../../main.tex]{subfiles}
\begin{document}


% \input{\subfix{images/Embedding_Models.tex}}
% \input{\subfix{tables/context_window.tex}}
\chapter{Ideas}
\section{Generation}
    \begin{enumerate}
        \item Duplicate question paper set generation given a paper and syllabus with maximum similarity and score them for similarity. RAG and multiagent. for each blooms level, for schools, maths, coding paper. extract from each question its key concepts and then use them to frame another similar question.
    \end{enumerate}
    
    \section{Question Generation}
        \begin{enumerate}
            \item Convert a text/paragraph into a fill in the blank question. Identify places which should be converted to blanks. Example To help student memorize a concept or story. 
            \item create a learning model(html component based) to generate learning content and render test say fill in the blank, mcq, short answer, etc. Which suggest areas to focus more and weakness.
            \item Generate possible confusions for a concept/text. Use feedback to determine confusions. Example for a question student might be confused and select non correct option. These confusions should determine area to focus. 
            \item For a give text/topic/content, extract/generate goals(learning paths) to reach expert level. Identify stages/goals and logically arrange them to reach expert level starting from novice. Example you should know A then B then C and so on till T to get full understanding of a topic.
            \item choose a method to extract topics from input docs to generate mcqs. 
            \item generate flow charts
            \item generate questions based on flow charts
            \item generate images, diagrams, flowcharts given a 
        \end{enumerate}

\end{document}